---
title: "INFO 201 Assignment 3"
author: "Minsuh Kim"
date: "2/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../source/analysis.R")
```

###### **Introduction**
Throughout history, the United States has a history of injustice and inequality,
especially in the topic of racism. The structures of over-policing and the "war
on drugs" have led to the discriminated arrests of people in color. This
assignment aims to reveal and analysis the bias and inequality within prison
incarcerations. In the assignment, I have chosen to analyze the jail and prison
population count, years, and states to calculate the amount of jailed people of
different races throughout the years and how they might differ within different
states. With these variables, I also decided to focus on the incarcerations of
both White and Black races in my data visualizations.

###### **Summary Information**
Looking through the data, I found that the highest number of jailed black people
ever recorded is **13,143.92** and the highest number of jailed white people
ever recorded is **7036.59**. The data also shows that **California** has the
highest total jailed population for both white and black people. While looking
through the total jail admissions, the highest recorded number of admissions
is **405,727** in 1988. While calculating the total jailed and imprisoned 
populations for the two races in different years, the results I received
describe that there are a total of **247,547** black people and **346,061.8**
white people in jail in 2018. For the population of imprisoned people, there are
**405,266** blacks and **415,876** whites in prison in 2016.

###### **Trends Over Time Chart:** 

```{r trends, echo=FALSE}
data_trends
```

I decided to choose this chart because I wanted to show the trend of how the
black and white prison population counts has changed over time. To do this,
I created a grouped bar chart with the dates filtered between 1990 and 2016.
I also calculated the total prison population for each race by year to find the
trends. From this chart, it shows that black prison populations started off with
an extremely high count around the beginning years and white prison populations
are low at the start and then gradually increases as the years progress.

###### **Variable Comparison Chart:** 
```{r compare, echo=FALSE}
data_compare
```

I decided to choose this chart because I wanted to look at how each race are
impacted by the jail population. To do this, I created a stacked bar chart that
compares the total jail population for whites and blacks through the geographic
locations of urbanicity. From what I can find, this chart shows a pattern in
which jailed black populations in urban areas are higher than jailed white
populations while white populations in rural areas are higher than black
populations.

###### **Map:**
```{r map, echo=FALSE}
data_map
```

I decided to choose this map because I wanted to measure how different the black
prison populations are in each state. To do this, I created a choropleth map of
the United States and calculated the overall total of black prison populations
throughout every year in each state. What I found in this map is that several
states in the Southern area have the highest black populations affected by the
prison system with California, Texas, and Florida to be some of the prominent
examples.